\demes: a pain-free specification for complex demography

### 2021-06-15 paper.tex
Apply suggestions from code review
Co-authored-by: Graham Gower <graham.gower@gmail.com>

% Add a bit more space between rows.
\renewcommand{\arraystretch}{1.5}
\begin{table}
\begin{center}
\begin{tabular}{lp{12cm}}
\toprule
\multicolumn{2}{l}{Software infrastructure}\\
\midrule
\texttt{demes-python} &
    A Python library for loading, saving, and working with
    Demes models. Includes conversion utilities for existing formats
    demographic model descriptions such as
    \texttt{ms}~\citep{hudson2002generating}.\\

@@

\stdpopsim &
    A collection of community empirical data for species
    and demographic models specified in Demes
    format~\citep{adrion2020community}.\\

>>>>

% Add a bit more space between rows.
\renewcommand{\arraystretch}{1.5}
\begin{table}
\begin{center}
\begin{tabular}{lp{12cm}}
\toprule
\multicolumn{2}{l}{Software infrastructure}\\
\midrule
\texttt{demes-python} &
    A Python library for loading, saving, and working with
    Demes models. Includes conversion utilities for existing
    demographic model descriptions such as
    \texttt{ms}~\citep{hudson2002generating}.\\

@@

\stdpopsim &
    A community-maintained collection of empirical data for species
    and demographic models specified in Demes
    format~\citep{adrion2020community}.\\
